Community context determines competition/facilitation trade-offs in pollination systems

### 2019-04-26 paper/cover-letter.Rnw
Finish cover letter

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{phd-bibliography/pollen-competition.bib}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    University of Canterbury, \\
    New Zealand
}
\date{April 15, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Prof. Tim Coulson,\\
    Editorial Office,\\
    Ecology Letters
}
% Opening statement
\opening{Dear Professor Coulson,}
% Letter body

@@

In this manuscript we show that

The covering letter to the Editorial Office should succinctly describe why the enclosed work is novel, exciting and of general interest in ecology.

Additionally, the covering letter should include a clear statement of exactly how the present manuscript is outstandingly novel relative to recent work by the author or coauthors cited in the present submission.

Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
However the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.

>>>>

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{phd-bibliography/pollen-competition.bib}
\usepackage{geometry}
\geometry{textwidth=43em, textheight=52\baselineskip}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    University of Canterbury, \\
    New Zealand
}
\date{April 15, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Prof. Tim Coulson,\\
    Editorial Office,\\
    Ecology Letters
}
% Opening statement
\opening{Dear Professor Coulson,}
% Letter body

@@

In this manuscript, we show that the realised competition for pollination niche (which can also be viewed as a plant species strategy to minimise competition for pollination) is strongly determined by the community it belongs to.
Furthermore, we show that in pollination there is no free lunch and plants need to balance multiple trade-offs when minimising competition for pollination.
On the one hand, factors that increase the quantity of pollen deposited by animals may also decrease its purity (and vice-versa).
On the other, factors that increase both the quantity and purity do so only mildly and potentially only in the short-term.

Very few studies have previously investigated how competition for pollination affects the pollination service at the community level using \emph{empirical data}.
We do so and go one step beyond by collecting not only pollen-deposition data but also plant abundance, visitation, pollen transfer, phenology and traits.
This allowed us to investigate the relationship between pollination service and multiple ecological factors, and for the first time, quantify the competition for pollination realised niche of plant populations.

Most studies of pollination communities focus on the mutualistic aspects of plant-pollination communities.
Ours provides evidence that animal-mediated pollination is actually a fluid dance between competition and pollination, and as such call for a shift in the way we think about pollination in community ecology.

Lastly, please note that the data used in this manuscript has been previously published\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017} by one of the co-authors.
However, the enclosed work represents a novel contribution for all involved and no related work published, in press, or submitted during this or last year has been cited.
